\cvitem{
    \cvtimeloc{
        \cvtimerange{09/2016}{\present}
    } {
        Ann Arbor, MI
    }
} {
    \cvplace{
        School of Information, University of Michigan
    } {
        Assistant Professor
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{09/2015}{09/2016}
    } {
        Ann Arbor, MI
    }
} {
    \cvplace{
        School of Information, University of Michigan
    } {
        Post Doctoral Presidential Fellow
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{09/2008}{04/2015}
    } {
        Pittsburgh, PA
    }
}{
    \cvplace{
        Carnegie Mellon University (Human-Computer Interaction Institute)
    } {
        Graduate Student and researcher
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{03/2013}{06/2013}
    } {
        San Francisco, CA
    }
}{
    \cvplace{
        Advanced Technologies Labs, Adobe Systems, Research Intern
    } {
        Designed and developed InterState, an interactive editor for creating highly interactive interfaces. (C.08)
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{06/2011}{09/2011}
    } {
        San Francisco, CA
    }
}{
    \cvplace{
        Advanced Technologies Labs, Adobe Systems, Research Intern
    } {
        Developed and evaluated \say{Codelets}, interactive documentation intended to help developers use example code snippets. (C.04)
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{05/2009}{08/2009}
    } {
        San Jose, CA
    }
}{
    \cvplace{
        IBM Research, Almaden, Research Intern
    } {
        Developed Playbook, a system that turns Photoshop drawings into interactive prototypes through programming-by-demonstration, conducted informal interviews with designers to develop design requirements. (C.03)
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{01/2007}{08/2008}
    } {
        Cambridge, MA
    }
}{
    \cvplace{
        MIT Media Laboratory, Cognitive Machines Group, Researcher
    }{
        Annotated baseball footage to train a system that automatically determines context from video frame content, wrote scripts to automate statistic gathering, and developed a system to search for statistics with natural language. (T.01)
    }
}

\iffalse
\cvitem{
    \cvtimeloc{
        \cvtimerange{06/2006}{08/2006}
    } {
        New York, NY
    }
}{
    \cvplace{
        Bank of America Securities, Equity Capital Markets, Summer Analyst
    }{
        Analyzed and reported on financial data of public corporations and created weekly updates sent to corporate clients.
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{06/2005}{08/2005}
    } {
        Redmond, WA
    }
}{
    \cvplace{
        Microsoft Corporation, Software Development Engineering in Test Intern
    }{
        Developed internal testing tools using the .NET framework for the (now defunct) Project Max.
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{06/2004}{08/2004}
    } {
        Webster, NY
    }
}{
    \cvplace{
        Xerox Corporation, Engineer
    } {
        Evaluated printer driver handicap accessibility against government standards.
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{01/2004}{05/2004}
    } {
        Cambridge, MA
    }
}{
    \cvplace{
        MIT Media Laboratory, Cognitive Machines Group, Researcher
    } {
        Developed and tested software \& hardware to help improve the position awareness of Ripley, an anthropomorphic robot.
    }
}

\cvitem{
    \cvtimeloc{
        \cvtimerange{09/2003}{02/2004}
    } {
        Cambridge, MA
    }
}{
    \cvplace{
        MIT Media Laboratory, Smart Architectural Surfaces Group, Researcher
    } {
        Assembled, soldered, and organized \say{smart tiles} - interactive tiles.
    }
}
\fi