\underlinestudents{\cvitem {
} {
Note: The names of authors who were students at the time are \student{underlined} (including my name if I was a student at the time of publication).
}}

\cvitem{
    ~\\
    \honorable{}
    % \best{}
} {
    \textbf{Labels:}\\
    \textit{honorable mention for best paper award}
    % \textit{best paper award}
}

\cvitem{
}{
    \textbf{Approximate acceptance rates:}\\
    UIST: 22\%, CHI: 23\%, VL/HCC: 30\%, CSCW: 25\%, ICSE: 19\%
}

\subsection{Heavily-reviewed Conference Papers (C)}
% \subsection{Heavily-reviewed Conference Papers (C) and Journal Manuscripts (J)}

\cvitem{
    C.18\\
    % \pdflink{http://from.so/p/data_science_collaboration.pdf}\\
} {
    \student{Wang, Y.}, \student{Mittal, A.}, Brooks, C., \me{Oney, S.} (2019) How Data Scientists Use Computational Notebooks for Real-Time Collaboration 
    \textit{ACM Conference on Computer-Supported Cooperative Work and Social Computing (CSCW)}, Austin, TX, USA. November 9--13. to appear.
}

\cvitem{
    C.17\\
    \pdflink{http://from.so/p/immersive_authoring.pdf}\\
} {
    \student{Zhang, L.}, \me{Oney, S.} (2019) Studying the Benefits and Challenges of Immersive Dataflow Programming.
    \textit{IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC)}, Memphis, TN, USA. October 14--18. to appear.
}


\cvitem{
    \honorable{}
    C.16\\
    \pdflink{http://from.so/p/touchstate.pdf}\\
} {
    \me{Oney, S.}, \student{Krosnick, R.}, Brandt, J., Myers, B. (2019) Implementing Multi-Touch Gestures with Touch Groups and Cross Events. \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, Glasgow, Scotland. May 4--9.
}

\cvitem{
    C.15\\
    \pdflink{http://from.so/p/chatcodes.pdf}
} {
    \me{Oney, S.}, Brooks, C., Resnick, P. (2018) Creating Guided Code Explanations with chat.codes. \textit{ACM Conference on Computer-Supported Cooperative Work and Social Computing (CSCW)}, New York, NY, USA. November 3--7. Article 131.
}

\cvitem{
    C.14\\
    \pdflink{http://from.so/p/expresso.pdf}
} {
    \student{Krosnick, R.}, \student{Lee, S. W.}, Lasecki, W., \me{Oney, S.} (2018) Expresso: Building Responsive Interfaces with Keyframes. \textit{IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC)}, Lisbon, Portugal. October 1--4. pp 39--47.
}

\cvitem{
    C.13\\
    \pdflink{http://from.so/p/arboretum.pdf}
} {
    \me{Oney, S.}, \student{Lundgard, A.}, \student{Krosnick, R.}, Nebeling, M., Lasecki, W. (2018) Arboretum and Arbility: Improving Web Accessibility Through a Shared Browsing Architecture. \textit{ACM Symposium on User Interface Software and Technology (UIST)}, Berlin, Germany, October 14--17. pp 937--949.
}

\cvitem{
    \honorable{}
    C.12\\
    \pdflink{http://from.so/p/adasa.pdf}
} {
    \student{Lin, S.C.}, Hsu, C.H., Talamonti, W., Zhang, Y., \me{Oney, S.}, Tang, L., Mars, J. (2018) Adasa: In-Vehicle Digital Assistant for Advanced Driver Assistance Features. \textit{ACM Symposium on User Interface Software and Technology (UIST)}, Berlin, Germany, October 14--17. pp 531--542.
}

\cvitem{
    C.11\\
    \pdflink{http://from.so/p/codeon.pdf}
} {
    \student{Chen, Y.}, \student{Lee, S. W.}, \student{Xie, Y.}, \student{Yang, Y.}, Lasecki, W., \me{Oney, S.} (2017) Codeon: On-Demand Software Development Assistance \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, Denver, CO, USA May 6--11. pp 6220--6231.
}

\cvitem{
    C.10\\
    \pdflink{http://from.so/p/codemend.pdf}
} {
    \student{Rong, X.}, \student{Yan, S.}, \me{Oney, S.}, Dontcheva, M., Adar, E. (2016) CodeMend: Assisting Interactive Programming with Bimodal Embedding. \textit{ACM Symposium on User Interface Software and Technology (UIST)}, Tokyo, Japan, October 16--19. pp 247--258.
}

\cvitem{
    C.09\\
    \pdflink{http://from.so/p/ondemand_support.pdf}
} {
    \student{Chen, Y.}, \me{Oney, S.}, and Lasecki, W. (2016) Towards Providing On-Demand Expert Support for Software Developers. \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, San Jose, CA, USA, May 7--12. pp 3192--3203.
}

\cvitem{
    \label{pub:c_08}
    C.08\\
    \pdflink{http://from.so/p/interstate.pdf}
} {
    \student{\me{Oney, S.}}, Myers, B., Brandt, J. (2014) InterState: A Language and Environment for Expressing Interface Behavior. \textit{ACM Symposium on User Interface Software and Technology (UIST)}, Honolulu, HI, USA, October 5--8.  pp 263--272.
}

\cvitem{
    \honorable{}
    C.07\\
    \pdflink{http://from.so/p/zoomboard.pdf}
} {
    \student{\me{Oney, S.}}, \student{Harrison, C.}, \student{Ogan, A.}, \student{Wiese, J}. (2013) ZoomBoard: A Diminutive QWERTY Soft Keyboard Using Iterative Zooming for Ultra-Small Devices. \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, Paris, France, April 27 -- May 2. pp 2799--3002
}

\cvitem{
    C.06\\
    \pdflink{http://from.so/p/constraintjs.pdf}
} {
    \student{\me{Oney, S.}}, Myers, B., Brandt, J. (2012) ConstraintJS: Programming Interactive Behaviors for the Web by Integrating Constraints and States. \textit{ACM Symposium on User Interface Software and Technology (UIST)}, Cambridge, MA, USA, October 7--10. pp 229--238
}

\cvitem{
    C.05\\
    \pdflink{http://from.so/p/nl_api_method_specs.pdf}
} {
    \student{Pandita, R.}, Xiao, X., Zhong, H., Xie, T., \student{\me{Oney, S.}}, Paradkar, A. (2012) Inferring Method Specifications from Natural Language API Descriptions. \textit{International Conference on Software Engineering (ICSE)}, Z{\"u}rich, Switzerland, June 2--9. pp 815--825
}

\cvitem{
    \label{pub:c_04}
    C.04\\
    \pdflink{http://from.so/p/codelets.pdf}
} {
    \student{\me{Oney, S.}}, Brandt, J. (2012) Codelets: Linking Interactive Documentation and Example Code in the Editor. \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, Austin, TX, USA, May 5--10. pp 2697--2706
}

\cvitem{
    \label{pub:c_03}
    C.03\\
    \pdflink{http://from.so/p/playbook.pdf}
} {
    \student{\me{Oney, S.}}, Barton, J., Myers, B., Lau, T., and Nichols, J. (2011) Playbook: Revision Control \& Comparison for Interactive Mockups. \textit{International Symposium on End-user Development (IS-EUD)}, Torre Canne, Italy, June 7--10. pp 295--300
}

\cvitem{
    C.02\\
    \pdflink{http://from.so/p/chi2010_designers.pdf}
} {
    \student{Ozenc, K.}, \student{Kim, M.}, Zimmerman, J., \student{\me{Oney, S.}}, and Myers, B. (2010). How to Support Designers in Getting Hold of the Immaterial Material of Software. \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, Atlanta, GA, USA, April 10--15. pp 2513--2522
}

\cvitem{
    C.01\\
    \pdflink{http://from.so/p/firecrystal.pdf}
} {
    \student{\me{Oney, S.}}, Myers, B. (2009). FireCrystal: Understanding Interactive Behaviors in Dynamic Web Pages. \textit{IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC)}, Corvallis, OR, USA, September 20--24. pp 105--108
}

\subsection{Book Chapters (B)}
\cvitem{
    B.01\\
    \pdflink{http://from.so/p/eud_perspectives.pdf}
} {
    Myers, B., Ko, A., Scaffidi, C., \me{Oney, S.}, Yoon, Y.S., Chang, K, \student{Kery, M.B.}, and \student{Li, T.} (2016). Making End User Development More Natural, in \textit{Advances in End User Development}, pp 1--22
}

\subsection{Refereed Posters (P), Workshops (W), and Doctoral Consortiums (D)}

\cvitem{
    P.10\\
    \pdflink{http://from.so/p/recreational_tracking.pdf}
}{
    \student{Pandey, M.}, Nebeling, M., Park, S.Y., \me{Oney, S.} (2019). Exploring the Tracking Needs and Practices of  Recreational Athletes. Poster at \textit{PervasiveHealth}. Trento, Italy.
}

\cvitem{
    W.09\\
    \pdflink{http://from.so/p/HusData_notebooks.pdf}
}{
    \student{Wang, A.}, \me{Oney, S.}, Brooks, C. (2019). Redesigning Notebooks for Data Science Education. Human-Centered Study of Data Science Work Practices Workshop, \textit{ACM Conference on Human Factors in Computing Systems (CHI)}. Glasgow, Scotland.
}

\cvitem{
    W.08\\
    \pdflink{http://from.so/p/attention.pdf}
}{
    \student{Spinelli, L.}, \student{Pandey, M.}, \me{Oney, S.} (2018). Attention Patterns for Code Animations: Using Eye Trackers to Evaluate Dynamic Code Presentation Techniques. \textit{Programming Experience (PX/18)}. Nice, France.
}

\cvitem{
    W.07\\
    \pdflink{http://from.so/p/CI2016.pdf}
} {
    \student{Chen, Y.}, \me{Oney, S.}, Lasecki, W. (2016). Expert Crowd Support Systems for Software Developers. \textit{Collective Intelligence 2016}, New York, NY, USA June 1--3.
}

\cvitem{
    W.06\\
    \pdflink{http://from.so/p/euclase_live.pdf}
} {
    \student{\me{Oney, S.}}, Myers, B., Brandt, J. (2013). Euclase: A Live Development Environment with Constraints and FSMs. International Workshop on Live Programming, \textit{International Conference on Software Engineering (ICSE)}, San Francisco, CA, USA, May 19.
}

\cvitem{
    W.05\\
    \pdflink{http://from.so/p/creative_authoring_backtracking.pdf}
} {
    Myers, B., \student{\me{Oney, S.}}, \student{Yoon, Y.}, Brandt, J. (2013). Creativity Support in Authoring and Backtracking. Workshop on Evaluation Methods for Creativity Support Environments, \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, Paris, France, April 28.
}

\cvitem{
    D.04\\
    \pdflink{http://from.so/p/StephenOneyDoctoralConsortiumFinal.pdf}
} {
    \student{\me{Oney, S.}} (2011) Development Tools for Interactive Behaviors. \textit{Doctoral Consortium: International Symposium on End-user Development (IS-EUD)}, Torre Canne, Italy, June 7--10. pp 395--398
}

\cvitem{
    D.03\\
    \pdflink{http://from.so/p/StephenOneyVL_2010DocConsort.pdf}
} {
    \student{\me{Oney, S.}} (2010) Democratizing Computational Tools for Interaction Designers. \textit{Doctoral Consortium: IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC)}, Madrid, Spain, September 21--25. pp 249--250
}

\cvitem{
    D.02\\
    \pdflink{http://from.so/p/StephenOneyDocConsort.pdf}
} {
    \student{\me{Oney, S.}} (2009) Empowering Designers with Creativity Support Tools. Doctoral Consortium: IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC), Corvallis, OR, USA, September 20--24. pp 254--255
}

\cvitem{
    W.01\\
    \pdflink{http://from.so/p/StephenOney_CHI2009_ComputationalCreativitySupport.pdf}
} {
    \student{\me{Oney, S.}}, Myers, B., and Zimmerman, J. (2009). Visions for Euclase: Ideas for Supporting Creativity through Better Prototyping of Behaviors. Workshop on Computational Creativity, \textit{ACM Conference on Human Factors in Computing Systems (CHI)}, Boston, MA, USA, April 4
}

\subsection{Theses (T)}

\cvitem{
    \label{pub:t_02}
    T.02\\
    \pdflink{http://from.so/p/soney_hcii_2015.pdf}
} {
    \student{\me{Oney, S.}} (2015). Expressing Interactivity with States and Constraints. \textit{Carnegie Mellon Ph.D Thesis}, Pittsburgh, PA, USA, April.
}

\cvitem{
    \label{pub:t_01}
    T.01\\
    \pdflink{http://from.so/p/StephenOneyThesis.pdf}
} {
    \student{\me{Oney, S.}} (2008). Natural Language Search of Structured Documents. \textit{MIT M.Eng Thesis}, Cambridge, MA, USA, August.
}